Supporting Information

### 2015-08-18 ms.Rmd
possible problem with setting IFS for grep query. Need to unset afterwards?

# https://gist.githubusercontent.com/rmflight/3858973/raw/591ee603ce0996ac407902f7dd59520b35b3702a/tableFigureFuncs.r
pasteLabel <- function(preText, inObj, objName, insLink=TRUE){
	objNum <- inObj[objName]

	useText <- paste(preText, objNum, sep=" ")
	if (insLink){
		useText <- paste("[", useText, "](#", objName, ")", sep="")
	}
	useText
}

# this increments the counter, and gives a name to the number so we can reference it later
incCount <- function(inObj, useName){
	nObj <- length(inObj)
	useNum <- max(inObj) + 1
	inObj <- c(inObj, useNum)
	names(inObj)[nObj+1] <- useName
	inObj
}
figCount <- c("_"=0)
tableCount <- c("_"=0)

tableCat <- function(inFrame){
	outText <- paste(names(inFrame), collapse=" | ")
	outText <- c(outText, paste(rep("---", ncol(inFrame)), collapse=" | "))
	invisible(apply(inFrame, 1, function(inRow){
		outText <<- c(outText, paste(inRow, collapse=" | "))
	}))
	return(outText)
}

capwords <- function(s, strict = FALSE) {
    cap <- function(s) paste(toupper(substring(s, 1, 1)),
                  {s <- substring(s, 2); if(strict) tolower(s) else s},
                             sep = "", collapse = " " )
    sapply(strsplit(s, split = " "), cap, USE.NAMES = !is.null(names(s)))
}

@@

```{r lmdFigure}
figCount <- incCount(figCount, "f_lmdFigure")
f_lmdFigure <- "data/lmdFigure.pdf"
```

>>>>

@@

```{r lmdFigure}
figCount <- incCount(figCount, "f_lmdFigure")
```

### 2015-08-18 si.Rmd
possible problem with setting IFS for grep query. Need to unset afterwards?

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
output:
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

```{r Setup, include=FALSE, results="hide", warning=FALSE}

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

source('src/R/figures.R')

```

### Fuzzy *c*-means clustering

```{r mfuzz}
figCount <- incCount(figCount, "f_mfuzzCentroids")
print(f_mfuzzCentroids)

figCount <- incCount(figCount, "f_mfuzzPca")
f_mfuzzPca
```
